---
title: "Data Driven Dashboards with R"
output:
    html_document:
        toc: true
        toc_float: true
---

***

This project is an employee dashboard built with various tools in the __R__ language.  
The purpose of this undertaking is to provide an in depth dive into the world of dashboards.

I created this project in order to teach this to other people on the Udemy platform.  
  
***

## Custom Functions {.tabset}

### install_packages.R

### import_libaries.R
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(devtools)
library(xlsx)
library(shiny)
library(shinydashboard)
library(flexdashboard)
library(formattable)
library(DT)
library(magrittr)
library(highcharter)
library(htmlwidgets)
library(lubridate)
library(calheatmapR)
```

### read_data.R
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Index Sheet
df0 <- read.xlsx("employee_data.xlsx",
                 sheetIndex = 1,
                 startRow = 1,
                 header = TRUE)
# Employee #1
df1 <- read.xlsx("employee_data.xlsx",
                 sheetIndex = 2,
                 startRow = 4,
                 header = TRUE)
# Employee #2
df2 <- read.xlsx("employee_data.xlsx",
                 sheetIndex = 3,
                 startRow = 4,
                 header = TRUE)
# Employee #3
df3 <- read.xlsx("employee_data.xlsx",
                 sheetIndex = 4,
                 startRow = 4,
                 header = TRUE)
# Employee #4
df4 <- read.xlsx("employee_data.xlsx",
                 sheetIndex = 5,
                 startRow = 4,
                 header = TRUE)
# Employee #5
df5 <- read.xlsx("employee_data.xlsx",
                 sheetIndex = 6,
                 startRow = 4,
                 header = TRUE)# Employee #6
df6 = read.xlsx("employee_data.xlsx",
                sheetIndex = 7,
                startRow = 4,
                header = TRUE)
# Employee #7
df7 <- read.xlsx("employee_data.xlsx",
                 sheetIndex = 8,
                 startRow = 4,
                 header = TRUE)
# Employee #8
df8 <- read.xlsx("employee_data.xlsx",
                 sheetIndex = 9,
                 startRow = 4,
                 header = TRUE)
# Employee #9
df9 <- read.xlsx("employee_data.xlsx",
                 sheetIndex = 10,
                 startRow = 4,
                 header = TRUE)
# Employee #10
df10 <- read.xlsx("employee_data.xlsx",
                  sheetIndex = 11,
                  startRow = 4,
                  header = TRUE)
```

### generate_heatmap.R

    
```{r, echo=TRUE, message=FALSE, warning=FALSE}
generate_heatmap <- function(dat) {
    
    # Subset the desired columns from dataframe
    dat <- dat[,c('date', 'time')]
    
    # Parse date
    dat$date <- parse_date_time(dat$date, orders = "ymd")
    
    # Make sure latest entries are being shown by plotting the current year
    # 
    # Select year out of date
    year <- substr(tail(dat$date, 1), 1, 4)
    
    # Select month out of date
    month <- 12
    start_date <- (as.numeric(as.Date(paste0(year,"-01-01"))) * 24 * 60 * 60 * 1000)
    
    
    # Convert data to acceptable form, i.e to '$timestamp : value' form
    timestamp <- as.numeric(dat$date)
    value <- dat$time
    dat <- setNames(as.list(value), timestamp)
    
    # Create heatmap
    heatmap <- calheatmapR(data = dat, height = "100%") %>%
        chDomain(domain = "month", 
                 subDomain = "day",
                 start = start_date,
                 range = month,
                 cellPadding = 2,
                 cellSize = 10,
                 margin = 1) %>%
        chLegend(legend = seq(1, 10, 2),
                 colours = list(min = "#00000c", # Sky-Blue
                                max = "cyan", # Navy-Blue
                                empty = "black"),
                 cellSize = 15,
                 cellPadding = 5) %>%
        chLabel(
            width = 33,
            itemName = "Hour")
    return(heatmap)
}

generate_heatmap(df6)

```

&nbsp;

__Note__ I have found that there is a glitch with choosing 2017 as the current year and start_date. 

***
