---
title: Homepage
output:
    html_document:
        toc: true
        toc_float: true
---

***

```{r setup, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

Welcome to <span style="color:black">&#9797; </span><span style="color:#008cba"><b>Realm of Ouranos</b></span>, your resource for data science, my mathematical endeavours, my daybreak expression and initiative.

In the navigation bar at the top you'll find the following:

- __Math Madness__, a section devoted to mathematics, ranging from simple _Calculus_ to _A.I_.
- __Data Wizardry__, a section devoted to data science projects, methodologies, explanations and code implementations in _R_, _Python_ and _Julia_.
- __Powerlifters' Cave__, a section devoted to my powerlifting hobby and special metrics and designs of my invention to regulate my training.

***

## Current Projects  

### Data Science

- __Daybreak__ This personal research website. [GitHub Repo](https://github.com/ykashou92/project_daybreak)


- __Electronaut__ 

### Mathematics

__Die Singularität__

A book on the post-physical singularity that we call the self.

***

## Professional Development

I have been taking a lot of online courses as a form of formal learning to make use of my free time, learn something new and delve deeper into *Data Science*, *Computer Programming* and various other related subjects:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(xlsx)
library(formattable)

course_table <- read.xlsx("course_table.xlsx",
                 sheetIndex = 1,
                 startRow = 1,
                 header = TRUE)
names(course_table)[3] <- "Course Title"
library(knitr)
kable(course_table)
```

Number of courses completed so far =  __`r nrow(subset(course_table, Status == "Complete")) + 9`__

***
